---
title: "Create ROC curves in R"
author: "Thomas Evangelidis"
date: "20/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Paste below all your score files. The first two columns must be the molname and the score (**the lowest score the better, not the opposite!**). The code will ignore the rest of the columns, if they exist.

```{r scores}
RESULTS_FILES = c("data/SF1.scores",
                  "data/SF2.scores",
                  "data/SF3.scores",
                  "data/SF4.scores",
                  "data/SF5.scores"
)

```

Paste below the file with molecular bioactivities of all molecules. First column must be the molname and the second its bioactivity (1 or 0).

```{r activities}
ACTIVITIES_FILE = "data/activities"
```

Write the names that will be shown in the legend.
```{r names}
NAMES <- c("Scoring Function 1", "Sscoring Function 2", "Scoring Function 3", "Scoring Function 4", 
           "Scoring Function 5")
```

Define (i) a function to find the molnames that were scored successfully by all given scoring functions, and (ii) a function to read a score file and a file with the bioactivity of each molecule (0 or 1).

<!-- Save all custom functions into a file ('function_definitions.r') and load them into the R notebook. This is the only way to be able
to resuse custom functions in other chuncks. The first chunk reads in fun.R using knitr::read_chunk. Later on, you can define an empty chunk that has the identifier that was used in fun.R as its name. This will act as if the contents of fun.R were written directly in this file. As you see, you can also use fun() in later chunks. --> 
```{r,cache = FALSE, echo=FALSE}
knitr::read_chunk("function_definitions.r")
```


```{r common_molnames}
```
```{r count_actives_inactives}
```
```{r read_scores}
```

Load the required libraries and create ROC curve plots. Adjust the font sizes (first line below).

```{r plot}
par(cex.main=2.0, cex.lab=1.5) ; # <== CHANGE ME

library("ROCR")
library("hash")

COLORS <- rainbow(3*length(RESULTS_FILES))
COLORS <- COLORS[seq(3, length(COLORS), 3)]

valid_molnames <- common_molnames(RESULTS_FILES)  ; # molnames with scores by all scoring functions; only these will be used for plotting
# Count and print the number of actives and inactives that are common in all score files
num <- count_actives_inactives(ACTIVITIES_FILE, valid_molnames)
for (i in 1:length(RESULTS_FILES)) {
  pred = read_scores(RESULTS_FILES[i], ACTIVITIES_FILE, valid_molnames)
  perf = performance(pred, 'tpr', 'fpr')
  if (i==1) { plot(perf, add = FALSE, colorize = FALSE, lwd=3, col=COLORS[i], 
                   main=paste("ROC Curves (", num$actives, "actives,", num$inactives, "inactives)")) }
  else { plot(perf, add = TRUE, colorize = FALSE, lwd=3, col=COLORS[i]) }
}

AUCs = rep(0, length(RESULTS_FILES))
LNAMES = rep(0, length(RESULTS_FILES))
for (i in 1:length(RESULTS_FILES)) {
  pred = read_scores(RESULTS_FILES[i], ACTIVITIES_FILE, valid_molnames)
  auc = performance(pred, measure='auc')
  AUCs[i] = sprintf("%.3f", auc@y.values)
  LNAMES[i] = paste(NAMES[i], "(", AUCs[i],")")
  # print(paste(NAMES[i], "AUC-ROC=", auc@y.values))
}

abline(a=0, b=1, lty=2, lwd=3, col="black")
# Add legend
legend(0.62, 0.28, legend=LNAMES,
       col=COLORS, lty=1, cex=0.8)
```


The number in parenthesis after each name in the legend is the area under the ROC curve.

**IMPORTANT: You will need to adjust the last line `legend(...)` to have a legend with the right names at the right position.**



